Impact of Education on Entrepreneurship - Data Gathering and Analysis

### 2014-11-27 GEMDataSource.Rmd
Adding new dataset GEM2009

#

>>>>

### Create new data frame without unnecessary data
WayOfTeaching <- SupportiveTeaching[, c("NES10CRNAME", "NES10_D01_MEAN")]

## as.factor("WayOfTeaching")

##TWayofTeaching <- SupportiveTeaching[c("Australia", "Austria", "Belgium", "Canada", "Chile", "Czech Republic", "Denmark", "Estonia", "Finland", "France", "Germany", "Greece", "Hungary", "Iceland", "Ireland", "Israel", "Italy", "Japan", "Korea", "Luxemburg", "Mexico", "Netherlands", "New Zealand", "Norway", "Poland", "Portugal", "Slovak Republic", "Slovenia", "Spain", "Sweden", "Switzerland", "Turkey", "United Kingdom", "United States"),])
